# Multi-way Classifier with Quantified Uncertainty

Many classifiers provide an answer with no information about how good
the answer is.  This exercise uses Stan via Richard McElreath's
`rethinking` package to train a classifier that knows how to say,
"Uh... I can't really tell."

For the code below, if a library $X$ fails to load you can try,
`install.packages("X")` and Google for more information about the
package.

```{r}
library(rethinking)
library(tidyverse)
```

## Create fake data

First, create some very easy to classify data, using the four
Cartesian sectors.

```{r}
s1 <- rmvnorm(50, c(10,10), 0.5 * diag(2))
s2 <- rmvnorm(50, c(-10,10), 0.5 * diag(2))
s3 <- rmvnorm(50, c(-10,-10), 0.5 * diag(2))
s4 <- rmvnorm(50, c(10,-10), 0.5 * diag(2))
d <- cbind(1, s1)
d <- rbind(d, cbind(2, s2))
d <- rbind(d, cbind(3, s3))
d <- rbind(d, cbind(4, s4))
d <- data.frame(d)
names(d) <- c("sector", "x", "y")
d[sample(nrow(d), 10),]
```

It looks pretty easy to classify!

```{r}
ggplot(d, aes(x=x, y=y, color=factor(sector))) + geom_point()
```

(I didn't make `d$sector` a factor in the data frame, because later on
Stan wouldn't like that.  It likes integers.)

## Create a model

I don't really like models that treat one of the classes as the
reference, but that's the only kind of model I know how to use for
N-way classification right now.  So I guess sector one can be the
baseline.

It takes about thirty seconds to fit the model on my machine.  Part of
that is waiting for Stan's model-specific C++ code to be generated and
compiled.

```{r}
system.time(m <- map2stan(
  alist(sector ~ dcategorical(softmax(0, s2, s3, s4)),
    s2 <- a2 + b2*x + c2*y,
    s3 <- a3 + b3*x + c3*y,
    s4 <- a4 + b4*x + c4*y,
    c(a2,a3,a4, b2, b3, b4, c2, c3, c4) ~ dnorm(0, 5)
  ),data=d))
```

OK.  Now let's check that the model predicts sector three for the true
mean of the sector-three data.

```{r}
str(link(m, data.frame(x=-10, y=-10)))
```

