# Bayesian Test Quantities

Usually Bayesians like Andrew Gelman, Richard McElreath, and Jim
Savage don't use the Kalmogorov-Smirnov test to determine goodness of
fit.  In [*Bayesian Data Analysis, 3rd
ed.](http://www.stat.columbia.edu/~gelman/book/), the "Test Quantity"
is introduced and contrasted with the more familiar "Test Statistic."

A test statistic is made using fixed parameters, but a test quantity
results from all possible values of the parameters, weighted by their
probabilities.  That is, the posterior predictive distribution is used
to find the test quantities.

The recommendation is for the analyst to choose test quantities that
make sense based on the overall goals of the statistical inquiry at
hand.  Below we do that with the maximum breach size per year.  Before
using the model to predict the future, a check determines whether a
data-based test quantity is similar to test quantities from simulated
data drawn from the posterior predictive distribution.

## Finding the Posterior Predictive Distribution

The data is loaded as before.

```{r}
library(dplyr)
source("prep.R")
dd <- prep.data("~/data/privacyrights.org/select-all.csv")
d <- tbl_df(dd$prepped)
```

A new library, *lubridate*, facilitates the task of working with the
dates in the data set.  Again, if a library *foo* does not load, it
can be installed via `install.packages("foo")`.  The code below
creates a `t` column in the data frame to match the `t` variable used
by Edwards et al. in their unorthodox time series model.  (Most time
series models treat time as the unusual, one-way autocorrelated random
variable it is, not as an unqualified predictor variable in a linear
regression.)

```{r}
library(lubridate)
d <- d %>% mutate(date=mdy(Date.Made.Public))
```

Then by using Richard McElreath's *rethinking* package, it's easy to
use the powerful Stan probabilistic modeling tool.

```{r}
library(rethinking)
m.data <- data.frame(
       y=as.numeric(d$Total.Records),
       t=as.numeric(difftime(d$date, d$date[1], unit="weeks") / 52.25),
       kind=as.factor(d$Type.of.breach))

(m <- map(
     alist(
       log(y) ~ dnorm(mu, sigma),
       mu <- a + b * t,
       sigma ~ dunif(0, 50),
       a ~ dnorm(0, 10),
       b ~ dnorm(0, 10)),
     data=m.data))
precis(m)
```

What does that look like?

```{r}
library(ggplot2)

ggplot(m.data, aes(t, log(y), color=kind)) +
  geom_point() +
  geom_abline(intercept=coef(m)["a"], slope=coef(m)["b"])
```

Noisy and flat, like the results in Edwards et al.
