# Checking for Fit

In ["Hype and Heavy Tails: A Closer Look at Data
Breaches"](http://www.econinfosec.org/archive/weis2015/papers/WEIS_2015_edwards.pdf),
2015, the authors use the Kolmogorov-Smirnov test to make sure that
their model selection should not be immediately rejected.  They
mention thick tails, but they don't use Student's t distribution for
log breach size.  They use the Gaussian.  But the t distribution has a
higher p-value in the K-S test.

```{r}
source("prep.R")
dd <- prep.data("~/data/privacyrights.org/select-all.csv")
d <- dd$prepped
xx <- as.numeric(d$Total.Records)
summary(xx)
```

How far out is that max?

```{r}
library(ggplot2)
qplot(xx)
tail(sort(xx))
```

It's pretty far out there, but not *too* crazy.  Can we rule out the
log normal distribution as a model for this data?

```{r}
y <- log(xx)
normal <- rnorm(length(y), mean(y), sd(y))
ks.test(y, normal)
```

No, Edwards et al. don't want to rule out the model when the p-value
is above 0.05.

Just out of curiousity, how's the t distribution with---say---five
degrees of freedom?

```{r}
t_dist <- rt(length(y), 5) * sd(y) + mean(y)
ks.test(y, t_dist)
```

Not as good.

So I think we can go ahead with log-normal as a model for breach size.

```{r}
library(tidyr)

df <- data.frame(
    log_size = y,
    t_dist = t_dist,
    normal = normal
) %>% gather()

ggplot(df, aes(value, color=key)) + geom_density()
```

They both look OK, and we *know* that some number of degrees of
freedom will make the t distribution be indistinguishable from the
normal, but meh.